### 2016-06-24 sec5_spm.tex
An almost finished version
Continue to revise

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned replicate partitioning is based on the temporal dimension 
and results in groups of snapshots in each partition. ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
To resolve the limitations caused by the replicate partitioning, 
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMP patterns. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

@@

\begin{theorem}\label{THM:SPM_TM}
Given a candidate pattern $P=\{O:T\}$, if $\mathtt{sim}(P.T)=\emptyset$, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
\end{theorem}

@@

\subsubsection{Apriori Enumeration}
We then design the Apriori enumeration method to
systematically discover all valid patterns in a star.
During the enumeration, we refer a candidate pattern
$P$ as a $R$-candidate if $|P.O|=R$. The enumeration
method discover patterns in ``bottom-up'' order:
in iteration $i$,  all $(i+1)$-candidates grows
to $(i+2)$-candidates. Enumeration ends if no
further candidates can be generated.

The process of enumeration is shown 
in Algorithm~\ref{algo:apriori_mining}. As a start, 
each edge is treated as a $2$-candidate pattern, with the 
inverted list as the time sequence. These $2$-candidates
are kept in $\mathbf{G}$ as the ground set. During the algorithm,
we maintain a set of candidates $\mathbf{C}$. $\mathbf{C}$
is initialized as $\mathbf{G}$.

As a start, each edge is treated as

To systematically discover valid patterns in each star,

we enumerate all valid patterns in ``bottom-up" order: 
pattern candidates with smallest object sizes are enumerated
first and grew to pattern candidates with larger object sizes.
During the enumeration, we call a candidate pattern
$P$ a $R$-pattern, if $|P.O|=R$.  The enumerator takes
a star as input, and treat each edge as a $2$-pattern.

The input of
the enumerator is a star. Each edge
in the star is treated a $2$-candidate, with the inverted
list to be the time sequence.

we design the \emph{Apriori Mining} algorithm. We borrow
the terminologies in classic Aprirori algorithm: a candidate
pattern $P$ is called $R$-pattern if the $|P.O|=R$. In Aprirori,
candidates grows from $2$-pattern level by level.

To describe the algorithm, we call a candidate pattern $R$-pattern 
if the size of its object set is $R$.  Therefore, each edge
in the star is effectively a $2$-pattern. The intuition of Apriori mining
is the observation that $(R+1)$-patterns can be generated
from $R$-patterns and $2$ patterns. Thus, we may iteratively 
enumerate pattern candidates with all possible sizes.
In particular, initially, for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. 
During each iteration, we generate $(R+1)$-patterns by joining $R$-patterns 
with the $2$-patterns. Technically, the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$
generates a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Note that in $Sr_s$,
each $R$-pattern contains the object $s$, thus the join only 
grow a $R$-pattern at most to a $(R+1)$-pattern.
Our mining algorithm stops where no further patterns are generated. 
The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.

\begin{algorithm}
\caption{Apriori Mining}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State {$\mathbf{C} \gets \{\}$, $\mathbf{G} \gets \{\}$, $\mathbf{OT} \gets \{\}$}
\ForAll{$e(s,t) = T \in Sr_s$}
\State {$T' \gets \mathtt{sim}(e(s,t))$}
%\State{ $\mathtt{sim}(e(s,t)) $} 
\State {$\mathbf{G}.\mathtt{add}(\langle \{s,t\}: T' \rangle)$, unless $T' \neq \emptyset$}
\EndFor
\State {$\mathbf{C} \gets \mathbf{G}$}
\While{$\mathbf{C} \neq \emptyset$}
		\State {$\mathbf{N} \gets \{\}$, $U \gets \{\}$}
		\ForAll{$(c,g)\in \mathbf{C}$}
			\ForAll {$g \in \mathbf{G}$ }
				\State {$c' \gets \langle c.O \cup g.O: \mathtt{sim}(c.T \cap g.T )\rangle$}
				\State {$\mathbf{N}.add(c')$, unless $c'.T \neq \emptyset$}
			\EndFor
			\State $\mathbf{OT}.\mathtt{add}(c)$, if $c$ is not extended.
		\EndFor	
		\State $U \gets $ union of $n_i \in \mathbf{N}$
		\ForAll{$n \in \mathbf{N}$}
			\State $U.O \gets$,  $U.T \gets U.T \cap n.T$
		\EndFor
		\If{$U$ is valid}
			\State $\mathbf{Output}.\mathbf{add}(U)$
			\State break;
		\EndIf
		\State {$\mathbf{C} \gets \mathbf{N}$}
		\State {Lv $\gets$ Lv $\oplus $ Ground} \Comment{ Simplification}
		\State {Remove false patterns in Lv}
		\Comment{Monotonicity}
		\If{union of Lv is a valid pattern}\Comment{Forward Closure}
			\State{output.add(Lv)} 
			\State{break}
		\EndIf
\EndWhile
\State output.addAll($Lv$)
\State \Return output
\end{algorithmic}
\end{algorithm}

An illustration of Algorithm~\ref{algo:apriori_mining} is shown in Figure~\ref{fig:star_partition} (c).
As shown, the star $Sr_3=\{3,4,5,6\}$ initially generate three $2$-candidates. At every iteration, 
higher level candidates are generated by joining lower level candidates. When no more candidates 
can be generated, the algorithm stops by outputting the valid patterns.
%
%It is notable that, in star partition, original data is 
%replicated at most $O(|\mathbb{O}|)$ times.
%In later sections, we will describe several 
%more optimization techniques to further reduce the amount of replicated data.

%In such a way, 
%given an object $u$, all the objects potentially
%co-moved with $u$ are captured in $u$'s neighborhood, which
%forms a \emph{star} structure in graph terms. SPM utilizes
%such structures to partition objects and then adapts an Apriori 
%algorithm to discover true GCMPs from each partition.

EXPLAIN CLEARLY HOW YOU IMPLEMENT THE FORWARD CLOSURE CHECKING! BETTER SHOW IT IN THE ABOVE PSEDUDO CODE IN THE APRIORI ALGORITHM.

Although leveraging \emph{temporal monotonicity} could largely prune
false candidates and reduce the apriori search space, 
it is ineffective when a \textit{true} pattern exists. 
In an extreme case, if a final pattern of a star $Sr_s$ is 
the \textit{union of all vertices} in the star,
then in apriori, ${|Sr_s|}\choose{i + 1}$ candidates needs to be generated at 
each level $i$. This results in an exponential search space while
the output only contains one pattern.  
Generally, when candidates at level $i$ collectively forms a true pattern, 
running aprior produces many wasted candidates.

Let $Lv_i$ be the set of candidates at level $i$ of Algorithm~\ref{algo:apriori_mining},
we use the \emph{forward closure} $FC_i$ to denote the union of the objects in
all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
\begin{theorem}[Forward Closure Checking]
\label{THM:SPM_FCC}
Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
and directly output $FC_i$.
\end{theorem}

It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
reduces, thus the terminating power of $FC$ would be stronger. We give hybrid example of the three
optimization as follows:
%To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
%quickly determine whether it is sufficient to terminate the apriori search. Given the candidates at
%level $i$ $Lv_i$, we define the \emph{forward closure} of $Lv_i$ as the union of objects from
%all candidates. Then, the following \emph{forward closure checking} rule can be used:
%
%\begin{theorem}[Forward Closure Checking Rule]
%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining}, the forward closure
%is $\mathbb{F}_i = \cup_{cand \in Lv_i} (cand.O) $. Algorithm~\ref{algo:apriori_mining} terminates when 
%$FC_i$ forms a valid GCMP .
%\end{theorem}

\begin{example}
We use Figure~\ref{fig:star_partition} (c) to 
demonstrate the power of candidate pruning. 
As shown, at the initial stage, $\{3,6:3\}$ is first pruned by \textit{Edge Simplification} since its
timestamps fails to be a candidate sequence. Subsequently, all further candidates containing $\{3,6\}$ 
are pruned by \textit{Monotonicity}. Then, we check the \textit{Forward Closure} 
of remaining candidates (i.e., $\{3,4\}$ and $\{3,5\}$) and find $\{3,4,5\}$ is a
valid candidate. Therefore, $\{3,4\}$ and $\{3,5\}$ are pruned, and $\{3,4,5\}$ is the output.
\end{example}

\subsection{Correctness of SPARE}
We summarize the workflow of SPARE framework in Figure~\ref{fig:star_partition} as follows. After the parallel clustering in each snapshot, we build an aggregated graph $G_A$ to capture the clustering relationship. In the map phrase, we partition $G_A$ into stars and emit the star partitions to the reducers. Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a pattern candidate $\{o,i: e(o,i)\}$ is created. Then the Apriori algorithm enumerate the true patterns from the candidate patterns. Meanwhile, the \emph{simplification}, \emph{monotonicity pruning} and \emph{forward closure checking} are applied to boost the enumeration process.
\eat{ ADD THE DETAILS WHEN THE REDUCER RECEIVE THE STAR PARTITIONS. HOW THEY DERIVE THE FINAL RESULT PATTERNS.}

\eat{
\begin{algorithm}
\caption{Star Partition and Mining}
\label{algo:spm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {---Map phase---}
\label{code:spm-map-start}
\ForAll{$C \in S_t$}
	\ForAll {$(o_1 ,o_2) \in C \times C$}
		\If{$o_1 < o_2$}  \label{code:spm-edge-direct}
			\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet
		\EndIf
	\EndFor
\EndFor
\label{code:spm-map-end}

@@

\State {---Reduce phase---}
\label{code:spm-reduce-start}
\ForAll{$\langle o, Sr_{o} \rangle$}
\State Apriori($Sr_o$)
\EndFor
\label{code:spm-reduce-end}

\end{algorithmic}
\end{algorithm}
}

In the following, we show the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}
If $P$ is a valid pattern in original trajectories, 
let $s$ be the object with smallest ID in $P.O$. 
Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
It follows that all object $o \in P.O$ are in $Sr_s$. 
Furthermore, every timestamp in $P.T$ is included
in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$. This ensures the \emph{completeness}. For any pattern $P$ enumerated by SPARE, by definition of star partition, $\forall o_1, o_2 \in P.O$, $\forall t \in P.T$, $C_t(o_1) = C_t(o_2)$. This ensure the \emph{soundness}.
\end{proof}.

In fact, besides that every valid patterns can be
mined in some stars, star partition further ensures
that patterns discovered
from different star partitions cannot be the same. 
This can be formulated as:

\eat{It is also interesting to observe that no duplicate patterns will be generated from the star partitions.}
\begin{lemma}[Pattern Uniqueness of Star Partition]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \not\equiv p_j.O$.
\end{lemma}
\begin{proof}
The correctness of Lemma~\ref{LEM:SPM_CORRECT} can be directly derived from the above arguments:
let $o_i$ be the smallest element in $p_i.O$ and $o_j$ be the smallest element in $p_j.O$. 
Since $p_i$ and $p_j$ belongs to different stars, then $o_i \neq o_j$, 
therefore $p_i.O \not\equiv p_j.O$. This proves the lemma.
\end{proof}

This lemma verifies the superiority of the SPARE framework over the TRPM framework.

>>>>

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned replicate partitioning is based on the temporal dimension which suffers from two drawbacks. First, the replication relies on $\eta$ which could be large. Second, the same valid pattern may be discovered from different partitions which results in redundant works.
%and results in groups of snapshots in each partition.
% ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
To resolve the limitations caused by the replicate partitioning, 
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMP patterns. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

@@

\begin{theorem}[Monotonicity]\label{THM:SPARE_MONO}
Given a candidate pattern $P=\{O:T\}$, if $\mathtt{sim}(P.T)=\emptyset$, then any pattern candidate $P'$ with $P.O \subseteq P'.O$ can be pruned.
\end{theorem}

@@

\subsubsection{Apriori Enumeration}
We design an Apriori enumeration method to efficiently discover all the valid patterns in a star partition. The principle of Apriori algorithm is to construct a lattice structure and enumerate all the possible candidate sets in a bottom-up manner. Its merit lies in the monotonic property such that if a candidate set is not valid, then all its supersets can be pruned. Thus, it works well in practice in spite of the exponential search space.

Our customized Apriori Enumerator is presented in Algorithm~\ref{algo:apriori_mining}. Initially, the edges (pairs of objects) in the star constitute the bottom level (Lines~\ref{code:init-start}-\ref{code:init-end}) and invalid candidates are excluded (Line~\ref{code:simp1}). An indicator \emph{level} is used to control the object size for candidate set join. During each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}), only candidates with object size equals to \emph{level} are generated (Line~\ref{code:join-start}). When two candidate sets $c_1$ and $c_2$ are joined, the new candidate becomes $c'=\langle c_1.O \cup c_2.O, c_1.T\cap c_2.T\rangle$ (Lines~\ref{code:join}). To check the validity of the candidate, we calculate $\mathtt{sim}(c'.T)$. If its simplified sequence is empty, $c'$ is excluded from the next level (Line~\ref{code:simp2}). This ensures that
then all the candidates with $P.O\supseteq c'.O$ are pruned. If a candidate cannot generate any new candidate, then it is directly reported as a valid closed pattern (Lines~\ref{code:output1-start}-\ref{code:output1-end}).
To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+,pei2000closet} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}). If yes, we can early terminate the algorithm and output the results.

\begin{algorithm}
\caption{Apriori Enumerator}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State {$C \leftarrow \emptyset$}
\ForAll{edges $c=\langle o_i\cup o_j, T_{o_i}\cap T_{o_j}\rangle$ in $Sr_s$} \label{code:init-start}
\If {$\mathtt{sim}(T_{o_i}\cap T_{o_j})\neq \emptyset$}
\State {$C\leftarrow C\cup \{c\}$} \label{code:simp1}
%\ElsIf{$c$ is a valid pattern}
%\State{output $c$}
\EndIf 
\EndFor\label{code:init-end}
\State $\mathrm{level} \gets 2$ \label{code:level}
\While{$C\neq \emptyset$} \label{code:level-start}
	\ForAll{$c_1 \in C$}
		\ForAll{$c_2 \in C$ and $|c_2.O \cup c_2.O| = \mathrm{level}$}\label{code:join-start}	
			\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}			
			\If{ $\mathtt{sim}(c'.T)\neq \emptyset$} \label{code:simp2}
					\State {$C'\leftarrow C'\cup \{c'\}$}
			\EndIf			
		\EndFor\label{code:join-end}
		\If {no $c'$ is added to $C'$} \label{code:output1-start}
			\If{$c_1$ is a valid pattern}
				\State output $c_1$
			\EndIf
		\EndIf \label{code:output1-end}
	\EndFor
%	
%		\ForAll{pairs $c_1\in C$, $c_2\in C$ and $c_1\neq c_2$} \label{code:join-start}
%				\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}
%				\If{ $\mathtt{sim}(c_1.T \cap c_2.T )\neq \emptyset$}
%					\State {$C'\leftarrow C'\cup \{c'\}$}
%					\ElsIf{$c'$ is a valid pattern}
%						\State{output $c'$}
%				\EndIf
%		\EndFor	\label{code:join-ends}
	\State $O_u \gets $ union of $c.O$ in $C$	\label{code:fc-checking-start}
	\State $T_u \gets $ intersection of $c.T$ in $C$	
	\If {$\langle O_u, T_u\rangle$ is a valid pattern}
		\State{output $\langle O_u, T_u\rangle$} \label{code:fc-checking}
		\State break;
	\EndIf \label{code:fc-checking-end}
	\State {$C\leftarrow C';C'\leftarrow \emptyset; \mathrm{level} \gets \mathrm{level}+1$}	
\EndWhile\label{code:level-ends}
\State output $C$ \label{code:output2-end}
\end{algorithmic}
\end{algorithm}

\begin{example}
As shown in Figure~\ref{fig:star_partition}(c), in the bottom level of the lattice structure, candidate $\{3,6:3\}$ is pruned because its simplified sequence is empty. Thus, all the object sets containing $\{3,6\}$ can be pruned. The remaining two candidates (i.e., $\{3,4:1,2,3\}$ and $\{3,5:2,3\}$)  derive a new  $\{3,4,5:2,3\}$ which is valid. By the forward closure checking, the algorithm can terminate and output $\{3,4,5:2,3\}$ as the final closed pattern.
\end{example}

\subsection{Put It Together}
We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows. After the parallel clustering in each snapshot, for ease of presentation, we used an aggregated graph $G_A$ to capture the clustering relationship. However, in the implementation of the map phrase, there is no need to create $G_A$ in advance.  Instead, we simply need to emit the edges within a star partition to the same reducer.  Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a candidate pattern $\{o,i: e(o,i)\}$ is created. Then it enumerates all the valid patterns from the candidate patterns. The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.

\begin{algorithm}
\caption{Star Partition and ApRiori Enumerator}
\label{algo:spm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {---Map phase---}
\label{code:spm-map-start}
\ForAll{$C \in S_t$}
	\ForAll {$o_1 \in C,  o_2 \in C, o_1 < o_2$}
	\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet~\label{code:spm-edge-direct}
	\EndFor
\EndFor
\label{code:spm-map-end}

@@

\State {---Reduce phase---}
\label{code:spm-reduce-start}
\ForAll{$\langle o, Sr_{o} \rangle$}
\State AprioriEnumerator($Sr_o$)
\EndFor
\label{code:spm-reduce-end}

\end{algorithmic}
\end{algorithm}

Compared with TPMP, the SPARE framework does not rely on snapshot replication to guarantee correctness. In addition, we can show that the patterns derived from a star partition are unique and there would not be duplicate patterns mined from different star partitions.
\begin{theorem}[Pattern Uniqueness]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \neq p_j.O$.
\end{theorem}
\begin{proof}
We prove by contradiction. Suppose there exist $p_i \in P_i$ and $p_j \in P_j$ with the same object set. Note that the center vertex of the star is associated with the minimum id. Let $o_i$ and $o_j$ be the center vertices of the two partitions and we have $o_i=o_j$. However, $P_i$ and $P_j$ are different stars, meaning their center vertices are different (i.e., $o_i\neq o_j$), leading to a contradiction. 
\end{proof}

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we prove the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}
See Appendix XXXX.
\end{proof}

### 2016-06-24 sec7_experiment.tex
An almost finished version
Continue to revise

@@

\textbf{Number of patterns under different parameters}: Figures~\ref{exp:patterns_vary}
\begin{figure}[h]
\centering
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_L.eps}
        \caption{Number of patterns vary $L$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_G.eps}
        \caption{Number of patterns vary $G$}
    \end{subfigure}    
\caption{Number of patterns discovered in three datasets on different parameters}
\label{exp:patterns_vary}
\end{figure}

\subsubsection{Detail comparison between SPARE and TRPM}

\subsection{SPARE Analysis}

\subsubsection{Scalability}
\begin{figure}[h]
\centering
   \includegraphics[width=0.45\textwidth]{/exp/spare/scalability.eps}
\caption{Scalability of SPARE vary. $N$ under different datasets.}
\label{exp:patterns_vary}
\end{figure}

\subsubsection{Load Balance}

>>>>

\textbf{Algorithms}: We implement TRPM, SPARE and SPARE-LB for comparison study. TRPM and SPARE are implement as described in Section 4 and 5. SPARE-LB extends SPARE by appending an additional load balance stage to the map phase. 
When the mapers complete, SPARE-LB collects the size of stars from all mappers. 
Then the best-fit strategy is applied for task allocation. In best-fit, 
tasks are assigned in decreasing order of their sizes, and the biggest 
unassigned task is allocated to the current mostly empty reducer. 
In SPARE-LB, we simply use the edge size of stars as an estimation of tasks. The other
part of SPARE-LB is identical with SPARE.

\textbf{Number of patterns under different parameters}: Figures~\ref{exp:patterns_vary} presents
 the number of valid GCMP patterns exist in the three datasets. Since the $M$,$K$,$L$,$G$
 impose different constraints on the patterns, the number of valid patterns changes as their 
 values change. We observe that $L$ has a great initial impact on the number of patterns
 discovered. As $L$ increases from $10$ to $20$, the number of patterns drops 50\%. As $L$
 increases further, the number of patterns decreases slowly. Opposed to $L$, when $G$
 is small, the number of patterns increases slowly. As $G$ reaches $30$, 
 the number of patterns nearly doubles. The distribution of patterns under $G$ and $L$
 reveals that there are many companions in real life which are short and repetitive. We can
 either discover these patterns by adjusting property $L$ and $G$ in the GCMP model.

\begin{figure}[h]
\centering
 	 \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_M.eps}
        \caption{Number of patterns vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_K.eps}
        \caption{Number of patterns vary $K$}
    \end{subfigure}  
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_L.eps}
        \caption{Number of patterns vary $L$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_G.eps}
        \caption{Number of patterns vary $G$}
    \end{subfigure}    
\caption{Number of patterns discovered in three datasets on different parameters}
\label{exp:patterns_vary}
\end{figure}

@@

%\subsubsection{Anatomy of SPARE and TRPM}

\subsection{SPARE Analysis}
Since SPARE is superior than TRPM,
we further analyze the SPARE in terms of its power of pruning, load balance
and scalablity.

\subsubsection{Power of sequence simplification}
One of the core techniques used in SPARE is the \emph{sequence simplification} (see Section 5.2.1). 
As shown in  Algorithm~\ref{algo:apriori_mining}, we use $\mathtt{sim}(T)$
to prune false candidates. To study the power of sequence simplification,
we collect the total number of initial pairs that are pruned. The
statistics are shown in Table~\ref{tbl:pruning} under default parameters. As the table
shows, the \emph{sequence simplification} is a very powerful pruning technique.
It cuts off near 90\% of the initial pairs, which significantly reduces the costs
in Apriori Enumeration. This confirms the necessity of design such a technique.
\begin{table}[h]
\begin{tabular}{|l|c|c|c|}
\hline 
\textbf{Data Set} & \textbf{Shopping} & \textbf{Geolife} & \textbf{Taxi} \\ 
\hline 
Before pruning & 878,309 &  1,134,228 & 2,210,101 \\ 
\hline 
After pruning & 76,672 & 123,410 & 270,921 \\ 
\hline 
Prune ratio & 91.2\% & 89.1\% & 87.7\% \\ 
\hline 
\end{tabular} 
%
%\begin{tabular}{|c|c|c|c|}
%\hline 
%\textbf{Dataset} & \textbf{Initial Candidates} & \textbf{Real Candidates} & \textbf{Prune-Ratio} \\ 
%\hline 
%Shopping & 878,309 & 76,672 &  91.2\%\\ 
%\hline 
%Geolife & 1,134,228 & 123,410 & 89.1\% \\ 
%\hline 
%Taxi & 2,210,101 & 270.921 & 87.7\% \\ 
%\hline 
%\end{tabular} 
\caption{Pruning power of SPARE}
\label{tbl:pruning}
\end{table}

\subsubsection{Load Balance}
We first compare SPARE and SPARE+ by analyzing the running time at
each map-reduce stage. The detail anatomy is shown in Figure~\ref{exp:wl}(a).
We can see that for both SPARE and SPARE-LB on three datasets, the reduce 
time takes the majority. The overall improvement of SPARE-LB is around 10-13\%
under default settings. We observe that the mapping and shuffle time
of SPARE and SPARE-LB are identical, where SPARE-LB spends a very small portion 
of extra time (4\% of the total time)
in applying the best-fit strategy. The time spent is worthwhile
as in the reduce phase SPARE-LB saves around 20\% of the time. However, since 
the star sizes in SPARE is almost identical (due to Theorem~2), the best-fit
strategy does not win too much.

We then look at the workload distribution of SPARE and SPARE-LB on the
real datasets. We collect the statistics from executors
and report their reduce times in Figure~\ref{exp:wl}. The figure shows
 that SPARE-LB is able to provide a more balanced task allocation
 as compared to SPARE in all three cases. Since SPARE takes random assignment
of stars, it is likely to incur skewed workloads as many large stars 
may be assigned to the same executor. 
However, as bounded by Theorem~2, the difference between
SPARE-LB and SPARE is not very large. In general cases, SPARE-LB is preferred
as it offers more efficiency while takes only a small extra time in planning.

\begin{figure*}[t]
\centering
	\begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/detail.eps}
        \caption{Comparison between SPARE and SPARE-LB}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/wl-shopping.eps}
        \caption{Workload distribution in Shopping}
    \end{subfigure}
    \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/wl-geolife.eps}
        \caption{Workload distribution in Geolife}
    \end{subfigure}  
    \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/wl-taxi.eps}
        \caption{Workload distribution in Taxi}
    \end{subfigure}
\caption{Load balance of SPARE and SPARE-LB in real datasets}
\label{exp:wl}
\end{figure*}

\subsubsection{Scalability}
We then study the scalability of SPARE-LB from two aspects. First, given
the number of executors, we sample a subset of data from three datasets
and test the performance of SPARE-LB. The results are shown in Figures~\ref{fig:scalability-wl}.
\begin{figure}[h]
\begin{subfigure}[b]{0.22\textwidth}
\centering
    \includegraphics[width=\textwidth]{/exp/spare/scalability-vary-O.eps}
        \caption{Scalability vary $O$}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-vary-T.eps}
        \caption{Scalability vary $T$}
    \end{subfigure}
 \caption{Scalability of SPARE-LB wrt. different data sizes}
 \label{fig:scalability-wl}
\end{figure}

We further test the scalalbility of SPARE under different number of executors. 
The result on the three dataset is presented in Figure~\ref{exp:scalability}.
We can see that SPARE achieves good scalability under all three cases. 
For instance, for Taxi dataset, when the executors rises from 14 to 54, 
the performance improves 3.5 times which is almost linear to the increase of executors. 
Such a pattern also holds for other two datasets.
\begin{figure}[h]
\centering
   \includegraphics[width=0.3\textwidth]{/exp/spare/scalability.eps}
\caption{Scalability of SPARE-LB vary. $N$ under different datasets.}
\label{exp:scalability}
\end{figure}
